---
title: "Data Science With R"
author: "Raphael Pimentel"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output:
  html_document:
    highlight: textmate
    logo: logo.png
    theme: journal
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
    df_print: paged
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# imports

```{r}
library(tidyverse)
library(janitor)
library(skimr)
library(gtsummary)
library(summarytools)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(readr)
library(summarytools)
library(kableExtra)
library(knitr)
library(gridExtra)
```

# load data

```{r}
df <- read_csv("data/train.csv", col_names = TRUE)
glimpse(df)
```

# data cleaning

```{r}
df1 <- janitor::clean_names(df) %>% 
  rename(days_associated = vintage,
         health_annual_paid = annual_premium) %>% 
  mutate(
    across(where(is.character), tolower),
    driving_license = ifelse(driving_license == 1, 'yes', 'no'),
    previously_insured = ifelse(previously_insured == 1, 'yes', 'no'),
    response = ifelse(response == 1, 'yes', 'no'),
    vehicle_age = case_when(
      vehicle_age == "< 1 year" ~ "below_1_year",
      vehicle_age == "1-2 year" ~ "between_1_2_years",
      vehicle_age == "> 2 years" ~ "over_2_years"
    )
  ) %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(response = factor(response, levels = c('yes', 'no')),
         driving_license = factor(driving_license, levels = c('yes', 'no')),
         previously_insured = factor(previously_insured, levels = c('yes', 'no')),
         vehicle_damage = factor(vehicle_damage, levels = c('yes', 'no')))

glimpse(df1)

# save df_cleaned as RDS
saveRDS(df1, 'df_cleaned.rds')
```

## data types

```{r}
variable_classes <- tibble(variables = names(df1),
       type = unlist(lapply(df1, class))
)
variable_classes
```

# column description

```{r}
variables <- df1 %>% names()
description <- c(
  "Unique ID for the customer",
  "Gender of the customer",
  "Age of the customer",
  "Customer has DL (yes/no)",
  "Unique code for the region of the customer",
  "Customer already has Vehicle Insurance (yes/no)",
  "Age of the Vehicle",
  "Customer got his/her vehicle damaged in the past (yes/no)",
  "The amount customer needs to pay as premium in the year",
  "Anonymized Code for the channel of outreaching to the customer ie. Different Agents, Over Mail, Over Phone, In Person, etc.",
  "Number of Days, Customer has been associated with the company",
  "Customer is interested (yes/no"
)
df_description <- tibble(variables = variables,
       description = description)

kable(data.frame(df_description), format = 'html') %>% 
  kableExtra::kable_styling(bootstrap_options = 'striped',
                            full_width = FALSE)
```

# descriptive statistics

```{r}
df_cleaned <- readRDS('df_cleaned.rds')
glimpse(df_cleaned)
```

```{r}
skimr::skim(df_cleaned)
```

## general overview

```{r}
df_cleaned %>% 
  select(-id) %>% 
  tbl_summary(
    type = list(response ~ 'categorical',
                driving_license ~ 'categorical',
                previously_insured ~ 'categorical',
                vehicle_damage ~ 'categorical'),
    digits = list(all_categorical() ~ c(0, 2))
  )
```

## more detailed statistics

```{r}
numerical <- df_cleaned %>% 
  select(age, health_annual_paid, days_associated)
```

```{r}
descriptive_tab <- summarytools::descr(numerical, style = 'rmarkdown') %>% round(2)

kable(data.frame(descriptive_tab), format = 'html') %>% 
  kableExtra::kable_styling(bootstrap_options = 'striped',
                            full_width = FALSE)
```

## visualization

```{r}
# age
age_plt <- numerical %>% 
  ggplot(aes(x=age)) + 
  geom_histogram(aes(y = after_stat(density)), binwidth = 1,
                 color = 'gray', fill = 'lightblue', alpha = 0.5) +
geom_density(color="blue") +
  labs(x ='age', y='density', title= 'Customers \nAge Distribution') +
  theme_minimal()

# health_annual_paid
paid_plt <- numerical %>% 
  ggplot(aes(x=health_annual_paid)) + 
  geom_histogram(aes(y = after_stat(density)), binwidth = 10000,
                 color = 'gray', fill = 'lightblue', alpha = 0.5) +
geom_density(color="blue") +
  labs(x ='health_annual_paid', y='density', title= 'Customers \nPayments \nDistribution') +
  theme_minimal()

# days_associated
days_plt <- numerical %>% 
  ggplot(aes(x=days_associated)) + 
  geom_histogram(aes(y = after_stat(density)), binwidth = 10,
                 color = 'gray', fill = 'lightblue', alpha = 0.5) +
geom_density(color="blue") +
  labs(x ='days_associated', y='density', title= 'Customers Days \nAssociated \nDistribution') +
  theme_minimal()

gridExtra::grid.arrange(age_plt, paid_plt, days_plt, ncol = 3)
```

## categorical attributes

```{r}
num_names <- names(numerical)
categorical <- df_cleaned %>% 
  select(-id, -one_of(num_names))
```

```{r}
gender_plt <- categorical %>% 
  ggplot(aes(x=gender)) +
  geom_bar(aes(fill=gender)) +
  labs(x = 'gender', y='#', title='Customers \nGender') +
  theme_minimal()

driving_license_plt <- categorical %>% 
  ggplot(aes(x=driving_license)) +
  geom_bar(aes(fill=driving_license)) +
  labs(x = 'driving_license', y='#', title='Customers \nDriving License') +
  theme_minimal()

region_code_plt <- categorical %>% 
  ggplot(aes(x=region_code)) +
  geom_bar(aes(fill=factor(region_code)),
           show.legend=FALSE) +
  labs(x = 'region_code', y='#', title='Customers \nRegion Code') +
  theme_minimal()

previously_insured_plt <- categorical %>% 
  ggplot(aes(x=previously_insured)) +
  geom_bar(aes(fill=previously_insured)) +
  labs(x = 'previously_insured', y='#', title='Customers \nPreviously Insured') +
  theme_minimal()

vehicle_age_plt <- categorical %>% 
  ggplot(aes(x=vehicle_age)) +
  geom_bar(aes(fill=vehicle_age)) +
  labs(x = 'vehicle_age', y='#', title='Customers \nVehicle Age') +
  theme_minimal()

vehicle_damage_plt <- categorical %>% 
  ggplot(aes(x=vehicle_damage)) +
  geom_bar(aes(fill=vehicle_damage)) +
  labs(x = 'vehicle_damage', y='#', title='Customers \nVehicle Damage') +
  theme_minimal()

policy_sales_channel_plt <- categorical %>% 
  ggplot(aes(x=policy_sales_channel)) +
  geom_bar(aes(fill=policy_sales_channel),
           show.legend = FALSE) +
  labs(x = 'policy_sales_channel', y='#', title='Customers \nPolicy Sales Channel') +
  theme_minimal()

response_plt <- categorical %>% 
  ggplot(aes(x=response)) +
  geom_bar(aes(fill=response)) +
  labs(x = 'response', y='#', title='Customers \nResponse') +
  theme_minimal()

gridExtra::grid.arrange(gender_plt, driving_license_plt, region_code_plt, previously_insured_plt, vehicle_damage_plt, vehicle_age_plt, policy_sales_channel_plt, response_plt, ncol = 2, nrow = 4)
```

# hypothesis validation

```{r}
#read data cleaned
df_cleaned <- readRDS('df_cleaned.rds')
```

## 1) customers with HIGHER AGE are more likely to get car insurance (TRUE)

```{r}
#boxplot
age_boxplot <- df_cleaned %>% 
  ggplot(aes(x=response, y=age)) +
  stat_boxplot(geom = 'errorbar', width=0.6) +
  geom_boxplot(aes(fill=response), show.legend = FALSE) +
  labs(title='Age vs Response', y='Age', x='Response') +
  theme_bw()

ggsave('age_boxplot.jpg', plot=age_boxplot)

#histogram
age_plot <- df_cleaned %>% 
  ggplot(aes(x=age)) +
  geom_histogram(binwidth = 1, color='gray', fill='navy') +
  facet_wrap(vars(response), nrow=2, scales='free_y') +
  labs(y='Customers')
  ggtitle('Age Distribution')
  
ggsave('age_plot.jpg', plot=age_plot)
```

```{r}
df_cleaned %>% 
  select(age, response) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

### customers with medium age of 43 are more likely to get car insurance

## 2) women are more likely to get car insurance (FALSE)

```{r}
gender_plot <- df_cleaned %>% 
  select(response, gender) %>% 
  ggplot(aes(x=response)) +
  geom_bar(aes(fill=gender), position='dodge') +
  labs(title='Gender vs Response', x='Response', y='Customers') +
  theme_bw()

ggsave('gender_plot.jpg', plot=gender_plot)
```

```{r}
df_cleaned %>% 
  select(response, gender) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

### 61% are male and 39% are female

## 3) customers having new cars are more likely to get car insurance (FALSE)

```{r}
car_age_plot <- df_cleaned %>% 
  select(response, vehicle_age) %>% 
  ggplot(aes(x=response)) +
  geom_bar(aes(fill=vehicle_age), position='dodge') +
  labs(title='Vehicle Age vs Response', x='Response', y='Vehicle Age') +
  theme_bw()

ggsave('car_age_plot.jpg', plot=car_age_plot)
```

```{r}
df_cleaned %>% 
  select(response, vehicle_age) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

### customers with car age between 1 and 2 years are more likely to get car insurance (75%), while only 15% of the interested customers have a new car

## 4) customers with previous car damage are more likely to get car insurance (TRUE)

```{r}
car_damage <- df_cleaned %>% 
  select(response, vehicle_damage) %>% 
  ggplot(aes(x=response)) +
  geom_bar(aes(fill=vehicle_damage), position='dodge') +
  labs(title='Vehicle Damage vs Response', x='Response', y='Vehicle Damage') +
  theme_bw()

ggsave('car_damage.jpg', plot=car_damage)
```

```{r}
df_cleaned %>% 
  select(response, vehicle_damage) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

### customers with previous car damage are more likely to get car insurance (98%)

## 5) customers with previous car insurance are more likely to get car insurance (FALSE)

```{r}
insured <- df_cleaned %>% 
  select(response, previously_insured) %>% 
  ggplot(aes(x=response)) +
  geom_bar(aes(fill=previously_insured), position='dodge') +
  labs(title='Previously Insured vs Response', x='Response', y='Previously Insured') +
  theme_bw()

ggsave('insured.jpg', plot=insured)
```

```{r}
df_cleaned %>% 
  select(response, previously_insured) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

### only 0.3% of customers interested in car insurance have the car previously insured

## 6) interest is higher in customers with HIGHER ANNUAL HEALTH expenses (FALSE)

```{r}
#boxplot
expenses_boxplot <- df_cleaned %>% 
  ggplot(aes(x=response, y=health_annual_paid)) +
  stat_boxplot(geom = 'errorbar', width=0.6) +
  geom_boxplot(aes(fill=response), show.legend = FALSE) +
  labs(title='Annual Payment vs Response', y='Annual Payment', x='Response') +
  theme_bw()

ggsave('expenses_boxplot.jpg', plot=expenses_boxplot)

#histogram
expenses_plot <- df_cleaned %>% 
  ggplot(aes(x=health_annual_paid)) +
  geom_histogram(binwidth = 10000, color='gray', fill='navy') +
  facet_wrap(vars(response), nrow=2, scales='free_y') +
  labs(y='Customers')
  ggtitle('Expenses Distribution')
  
ggsave('expenses.jpg', plot=expenses_plot)
```

```{r}
df_cleaned %>% 
  select(response, health_annual_paid) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

### although the health annual paid showed to be significant, we can consider this hypothesis FALSE and will further investigate the outliers

## 7) customers with health insurance for more time are more likely to get car insurance (FALSE)

```{r}
#boxplot
days_boxplot <- df_cleaned %>% 
  ggplot(aes(x=response, y=days_associated)) +
  stat_boxplot(geom = 'errorbar', width=0.6) +
  geom_boxplot(aes(fill=response), show.legend = FALSE) +
  labs(title='Days Associated vs Response', y='Days Associated', x='Response') +
  theme_bw()

ggsave('days_boxplot.jpg', plot=days_boxplot)

#histogram
days_plot <- df_cleaned %>% 
  ggplot(aes(x=days_associated)) +
  geom_histogram(binwidth = 30, color='gray', fill='navy') +
  facet_wrap(vars(response), nrow=2, scales='free_y') +
  labs(y='Customers')
  ggtitle('Days Associated')
  
ggsave('days_plot.jpg', plot=days_plot)
```

```{r}
df_cleaned %>% 
  select(response, days_associated) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

### low relevance 

## hypothesis conclusion

```{r}
hypothesis <- c(
  '1) customers with HIGHER AGE are more likely to get car insurance',
  '2) women are more likely to get car insurance',
  '3) customers having new cars are more likely to get car insurance',
  
  '4) customers with previous car damage are more likely to get car insurance',
  '5) customers with previous car insurance are more likely to get car insurance',
  '6) interest is higher in customers with HIGHER ANNUAL HEALTH expenses',
  '7) customers with health insurance for more time are more likely to get car insurance'
  )

conclusion <- c(
  'True',
  'False',
  'False',
  'True',
  'False',
  'False',
  'False'
)

relevance <- c(
  'High',
  'Medium',
  'High',
  'High',
  'High',
  'Low',
  'Low'
)

hypothesis_table <- tibble(
  hypothesis = hypothesis,
  conclusion = conclusion,
  relevance = relevance
)

kable(hypothesis_table, format='html') %>% 
  kableExtra::kable_styling(bootstrap_options = 'striped', full_width = FALSE)
```
